Predictive modeling with cross validation

### 2017-08-11 model fitting/cross_validation.Rmd
used stepAIc with backwards/forward sepwise selection, added interaction terms, recoded category variable

#===================================================================
# if text contains any end punctuation
train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = train1)
summary(cr_containpun) # p=8.269e-09
identical(train1$text_contain_punct, train1$contain_punct)
#===================================================================
# if the text ends in a punctuation
train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = train1)
summary(cr_endpunct) # p=0.185

@@

### Backwards selection of variables

* using selectCox function from pec package
* choose between n_images or new_n_images
* weekday or is_weekend
* text_till_punct or text_contain_punct? 
* frequent_tag or num_freq_tags

```{r}
model1 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_till_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
summary(model1)
AIC(model1, k = 2) # 65065.97

# with new_n_images instead of n_images: 65072.75

# fitting is_weekend instead of weekday: 65066.88 - keep weekday
model2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_till_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
AIC(model2, k = 2)

# fitting with text_contain_punct instead of text_till_punct: 65061.46
model3 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
AIC(model3, k = 2) #  (keep text_contain_punct)

# text_contain_punct + is_weekend: 65063.91
model4 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
AIC(model4, k = 2) #  (keep text_contain_punct)

# fitting with num_prior_effect instead of prior effect: 65063.25
model5 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + num_prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
AIC(model5, k = 2)

# fitting with frequent_tag instead of avg_tag_score
# final model 
model6 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1)
AIC(model6, k = 2) # keep avg_tag_score
```

```{r}
model <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + is_weekend + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + avg_tag_score + contain_answered + contain_unanswered, data = train1, rule = "aic") # 65058.03

#results:
final1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + is_weekend + ampm + device_length + title_questionmark + update + avg_tag_score + contain_answered + contain_unanswered, data = train1)
summary(final1)

#added interaction term 
final <- coxph(Surv(time_until_answer, answered) ~ category + new_user + is_weekend + ampm + device_length + title_questionmark + title_beginwh + update + avg_tag_score + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update, data = train1)
AIC(final, k = 2) #65054.87  
summary(final)
```

### trying out a different stepwise function
```{r}
# variables <- c("category", "n_images", "n_tags", "new_user", "is_weekend", "ampm", "text_length", "device_length", "text_contain_punct", "title_questionmark", "title_beginwh", "capital_text", "text_all_lower", "prior_effort", "gratitude", "greeting", "update", "newline_ratio", "max_tagwords", "avg_tag_score", "contain_answered", "contain_unanswered")
# 
# modell <- My.stepwise.coxph(Time = "time_until_answer", Status = "answered", variable.list = variables, data = train1)
# #my.variable.list <- c("inst", "age", "sex", "ph.ecog", "ph.karno", "pat.karno", "meal.cal",
# levels(train1$category)[4] <- "CarTruck"
# levels(train1$category)[5] <- "ComputerHardware"
# levels(train1$category)[10] <- "MediaPlayer"
# levels(train1$category)[7] <- "GameConsole"
```

>>>>

#===================================================================
# if text contains any end punctuation
train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = train1)
summary(cr_containpun) # p=8.269e-09
identical(train1$text_contain_punct, train1$contain_punct)

#===================================================================
# if the text ends in a punctuation
train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = train1)
summary(cr_endpunct) # p=0.185

@@

### Fitting model with all significant variables (univariate analysis p-value < 0.01)

```{r}
first <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1)
summary(first)
AIC(first, k = 2) # 65065.88

# backwards step-wise selection with selectCox function
model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1, rule = "aic")
cox
#results
results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + contain_answered + contain_unanswered, data = train1)
AIC(results1, k = 2) #65059
summary(results1)

# backward/forward step-wise selection with stepAIC function from MASS package
model2 <- stepAIC(model, direction = "both", k = 2)
# results
results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1)
AIC(results2, k = 2) # 65050.45
summary(results2)

# best subset selection with glmulti function
# took out variables based off of p-value (function couldn't handle amount of predictors)
# model3 <- glmulti(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + capital_text + text_all_lower + prior_effort + greeting + update + newline_ratio + frequent_tag, 
#                 data = train1,
#                 level = 1, 
#                 method = "g", 
#                 crit = "aic",
#                 fitfunction = "coxph",
#                 confsetsize = 5
#                 )
# model3@formulas
# #results
# results3 <- coxph(Surv(time_until_answer,answered)~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + newline_ratio + frequent_tag, data = train1)
# AIC(results3) # 65098.48
# summary(results3)

# trying out lasso regularization with the glmnet package
# library(glmnet)
# setting up matrix for function
# mx <- as.matrix(train1 %>% 
#   tbl_df() %>%
#   dplyr::select(category, n_images, n_tags, new_user, weekday, ampm, text_length, device_length, text_contain_punct, title_questionmark, title_beginwh, capital_text, text_all_lower, prior_effort, gratitude, greeting, update, newline_ratio, max_tagwords, frequent_tag, contain_answered, contain_unanswered))
# model4 <- glmnet(x, y = Surv(train1$time_until_answer, train1$answered, type = "right"), family = "cox")
# summary(model4)
# 
# x <- model.matrix( ~ rx + sex + age + obstruct + perfor + adhere + surg - 1, d)
# 
# x <- model.matrix(~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered - 1, train1)
```

```{r}
# working with model from backward/forward stepwise selection
results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1) # 65050.45

# adding interaction terms
r2_i <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_i, k = 2) # 65037.36
summary(r2_i)
```

##### recoding category variable

* separate iPhones/Androids (or group all apple products together?) - use str_detect to find categories with apple/iphone/mac (since there are apple watches in the apparel category)
* keep Mac and PC the same
* group all categories that have less than 100 questions together? 
* group electronics + median player
* group household + appliance
* group car and truck + vehicle

```{r}
# pie chart of product categories
ggplot(train1, aes(x = factor(1), fill = category)) + geom_bar(width = 1) + 
  coord_polar(theta = "y")

train1 %>%
  group_by(category) %>%
  summarise(median_t = median(time_until_answer), n = n()) %>%
  arrange(median_t)

# recoding category variable
train1$new_category <- as.character(train1$category)
train1$new_category[train1$subcategory == "iPhone"] <- "iPhone"
train1$new_category[train1$new_category == "Phone"] <- "Android/Other OS Phone"
train1$new_category[train1$new_category == "Electronics" | train1$new_category == "Media Player"] <- "Electronics/Media"
train1$new_category[train1$new_category == "Household" | train1$new_category == "Appliance"] <- "Home"
train1$new_category[train1$new_category == "Car and Truck"] <- "Vehicle"

#if there are less than 50 questions in a certain category, group with "Other"
n <- train1 %>%
  group_by(category) %>%
  summarise(n = n())
# fix this (not working correctly)
for (i in nrow(n)) {
  if (n$n[i] < 50) {
    train1$new_category[train1$category == n$category[i]] <- "Other"
  }
}

# model with new_category- AIC dropped 
r2_new <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_new, k = 2) # 64743.48
summary(r2_new)
```

```{r}

```
